\section{Comparison to SSI Survey}
\label{sec:ssicompare}

This work was inspired by a UK survey led by the Software Sustainability Institute. While their findings are for the wider scientific community in the UK and ours are for the worldwide astronomical community, a comparison is still interesting. 

The SSI survey finds that 90\% of UK scientists use software in their research. Our survey shows that astronomy is in line with other sciences in the use of software --  100\% of astronomers use it. 90\% of astronomers write some software (93\% of UK astronomers). This is much larger than the SSI survey, which finds that only 56\% of researchers, across all disciplines, write some of their software.  This implies astronomers are much more dependent on their own software than other sciences.

In the SSI survey, 55\% of respondents say they have received some training in software development, with 40\% indicating that the training was a formal course and 15\% indicating self-directed study. Our categories are not identical, but we find that a similar fraction of astronomers -- 57\% (53\% of UK astronomers) -- say that they have received some form of training. However, only 8\% say that the training was substantial, while 49\% say they received a little training. The decision what constitutes a lot and a little was left to the participants. Those who chose to expand on their decision indicated that a lot corresponded to a formal class while a little corresponded to using on-line materials such as Software Carpentry and Code Academy.

Finally, 40\% of our survey respondents who predominantly write their own software have received no training (42\% of those who write some of their own software). This fraction is twice as large as the one reported in the SSI survey (21\%) and may indicate that in astronomy there are fewer efforts to train researchers in software development.  This is all the more surprising given that many \empf{more} astronomers write their own code, according to these surveys.



    
  
  
  